### 2016-04-01 text/ms.Rmd
Edit the introduction

Population status and trend are two of the most fundamental values to quantify in fisheries management [e.g. TODO NEW REFS]. However, fisheries managers are often faced with reconciling multiple uncertain and potentially conflicting estimates of status and trend [e.g. @brodziak2010; @branch2011; @deroba2015]. Some models may suggest a population is at risk and declining in abundance while others may suggest it is not at risk and stable.

One solution is to take the average or weighted average of several model predictions, i.e. an ensemble. Such ensembles are typically more accurate and less biased than individual model estimates and can integrate uncertainty in model structure, initial conditions, and parameter estimation [@dietterich2000; @araujo2007]. <!--explain how this is possible.--> This approach forms the basis of many machine learning methods [e.g. @dietterich2000], has helped reconcile climate forecasts from dozens of models [e.g. @murphy2004; @tebaldi2007; @ipcc2013], and even improved early warning signs of malaria outbreaks [@thomson2006]. In ecology, ensemble methods are sometimes used to improve species distribution modelling [e.g. @araujo2007; @breiner2015] and indeed have been used to combine estimates of population status and trend [e.g. @brodziak2010].

>>>>

Population status and trend are two of the most fundamental values to quantify in fisheries management [e.g. TODO NEW REFS]. However, fisheries managers are often faced with reconciling multiple uncertain and potentially conflicting estimates of status and trend [e.g. @brodziak2010; @branch2011; @deroba2015]. For example, some models may suggest a population is at risk and declining in abundance while others may suggest it is not at risk and stable.

One solution is to take the average or weighted average of several model predictions, i.e. an ensemble. Such ensembles are typically more accurate and less biased than individual model estimates and can integrate uncertainty in model structure, initial conditions, and parameter estimation [@dietterich2000; @araujo2007]. Ensembles are superior to individual models for at least three reasons including statistical, computational, and representational reasons [@dietterich2000]. Statistically by averaging across models representing different hypotheses about reality, computationally by reducing the risk of getting stuck in a local optima, and representationally he by expanding representational form<!--explain how this is possible.--> This approach forms the basis of many machine learning methods [e.g. @dietterich2000], has helped reconcile climate forecasts from dozens of models [e.g. @murphy2004; @tebaldi2007; @ipcc2013], and even improved early warning signs of malaria outbreaks [@thomson2006]. In ecology, ensemble methods are sometimes used to improve species distribution modelling [e.g. @araujo2007; @breiner2015] and indeed have been used to combine estimates of population status and trend [e.g. @brodziak2010].
